
---
title: "Growers report"
author: "CSIRO team"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document: default
---

```{r setup and load library, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(dplyr)
library(tidyverse)
library(readr)
library(lubridate)
library(DT)
library(sp)


library(rgdal)
library(sf)

#install.packages("plotKML")
library(plotKML)
library(knitr)
library(png)

library(readxl)


library(ggmap)
library(maps)
library(mapdata)

library(raster)
library(formattable)
library(magick)
library(readxl)

```

## Growers details
```{r define_sites, echo=FALSE, message=FALSE, warning=FALSE}



#######################################################################################################################################################
paddock_done2020_t<- read_excel("C:/Users/ouz001/OneDrive - CSIRO/Soil_Testing_Project/paddock_done2020.xlsx",
                                sheet = "T-test_done")



# paddock_done2020_t<- read_excel("w:/value_soil_testing_prj/Yield_data/2020/processing/paddock_done2020.xlsx", 
#                                 sheet = "T-test_done")

paddock_done2020_t <- paddock_done2020_t %>% 
  dplyr::mutate(paddock5_digits = substr(`Paddock code`, start = 1, stop = 5))

#select orgaiastion

selection_organisation <- "SFS"

selection_Contact <- "Ashley Amourgis"

selection_Farmer <- "Peel"


paddock_done2020 <- 
  #filter(paddock_done2020_t, Organisation %in% selection_Contact) %>% 
  filter(paddock_done2020_t, Contact %in% selection_Contact) %>% 
  #filter(paddock_done2020_t, Farmer %in% selection_Farmer) %>% 
  distinct(paddock5_digits, .keep_all= TRUE) %>% 
  dplyr::select(paddock = paddock5_digits,
                Organisation,
                Contact,
                Farmer,
                `Paddock tested`,
                'issues/ comments',
                'Rates excluded (recom rate analysis)' = Rates_excluded_rec_rate,
                'Rates used (low med high analysis)' = rate_used_low_high_med,
                `Dan's comments from reports` )   %>% 
  dplyr::arrange(Farmer) 

paddock_done2020_display <- 
  filter(paddock_done2020_t, Contact %in% selection_Contact) %>% 
  #filter(paddock_done2020_t, Farmer %in% selection_Farmer) %>% 
  distinct(paddock5_digits, .keep_all= TRUE) %>% 
  dplyr::select(Paddock = paddock5_digits,
                Organisation,
                Contact,
                Farmer,
                `Paddock tested`,
                'issues/ comments',
                `Dan's comments from reports`) %>% 
  dplyr::arrange(Farmer) 


paddock_details <- paddock_done2020_t %>% 
  dplyr::select(`Paddock code`,
                Farmer,
                `Paddock tested`,
                Zone) %>% 
  dplyr::mutate(paddock5_digits = substr(`Paddock code`, start = 1, stop = 5)) %>% 
  dplyr::mutate(paddock5_digits = as.double(paddock5_digits)) 



paddock_done2020_display %>% 
  formattable(align = "l", - 1  )


```

Extra Notes:

	

- Wills	Oroukes E	
  waiting for yield data to be extracted
  
- Wills	Oroukes W	
  waiting for yield data to be extracted
  
- Vallance	Naradoon East	
  Confirmed Map but no yield
  
- Vallance	Naradoon West	
  Confirmed Map but no yield
  
- Dennis	Ressi W	
  waiting for yield data to be extracted
  
- Dennis	Ressi E
  waiting for yield data to be extracted
  
- Keating	Middle Fays	
  Updated rates but there is a Nill and skinny 0? Need to contact to Ash to proceeded 
  I think we have yld data 
  
- Keating	Far Fays	
  Updated rates but there is a Nill and skinny 0? Need to contact to Ash to proceeded 
  I think we have yld data









```{r define_sites2, echo=FALSE, message=FALSE, warning=FALSE}


## set up some folder to look for data:

png_folder <- "W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/png"

Growers_folder <- paste0("W:/value_soil_testing_prj/Yield_data/2020/", 
                         unique(paddock_done2020$Organisation), "/",unique(paddock_done2020$Contact), "/")


Growers_folder <- gsub(" ", "_", Growers_folder)
Growers_folder <- gsub("-", "_", Growers_folder)

#Growers_folder <- "W:/value_soil_testing_prj/Yield_data/2020/FSG/MSF_Frontier_Farming/"

#each folder for the sites (4 listed here)
site1 <- paste0((unique(paddock_done2020$Farmer)[1]),"/",
                (unique(paddock_done2020$`Paddock tested`)[1]),
                #(unique(paddock_done2020$Farmer)[1]),
                "/output/")

 site2 <- paste0((unique(paddock_done2020$Farmer)[1]),"/",
                 (unique(paddock_done2020$`Paddock tested`)[2]),
                 #(unique(paddock_done2020$Farmer)[2]),
                 "/output/")
 
 site3 <- paste0((unique(paddock_done2020$Farmer)[1]),"/",
                 (unique(paddock_done2020$`Paddock tested`)[3]),
                 #(unique(paddock_done2020$Farmer)[3]),
                 "/output/")

 site4 <- paste0((unique(paddock_done2020$Farmer)[1]),"/",
                 (unique(paddock_done2020$`Paddock tested`)[4]),
                 "/output/")


  site5 <- paste0((unique(paddock_done2020$Farmer)[1]),"/",
                   (unique(paddock_done2020$`Paddock tested`)[5]),
                   "/output/")
 
  site6 <- paste0((unique(paddock_done2020$Farmer)[1]),"/",
                   (unique(paddock_done2020$`Paddock tested`)[6]),
                   "/output/")
 # 
 # site7 <- paste0((unique(paddock_done2020$Farmer)[2]),"/",
 #                  (unique(paddock_done2020$`Paddock tested`)[7]),
 #                  "/output/")



site1 <- gsub(" ", "_", site1)
site1 <- gsub("-", "_", site1)
site1 <- gsub("&", "_", site1)
#site1 <- gsub("/", "_", site1)
site2 <- gsub(" ", "_", site2)
site2 <- gsub("-", "_", site2)
site2 <- gsub("&", "_", site2)
site3 <- gsub(" ", "_", site3)
site3 <- gsub("-", "_", site3)
site3 <- gsub("&", "_", site3)
site4 <- gsub(" ", "_", site4)
site4 <- gsub("-", "_", site4)
site5 <- gsub("-", "_", site5)
site5 <- gsub(" ", "_", site5)
site6 <- gsub("-", "_", site6)
site6 <- gsub(" ", "_", site6)
# site7 <- gsub("-", "_", site7)
# site7 <- gsub(" ", "_", site7)



#Growers_folder 
# site1
# site2
# site3
# site4
# site5

#Lets look for a yld trace maps

#list files that conatin the word "trace" followed by anything and ending with the word ".png":
yld_trace_site1 <- list.files(path = paste0(Growers_folder, site1),pattern = "trace(.*)$", ignore.case = TRUE)
yld_trace_site2 <- list.files(path = paste0(Growers_folder, site2),pattern = "trace(.*)$", ignore.case = TRUE)
yld_trace_site3 <- list.files(path = paste0(Growers_folder, site3),pattern = "trace(.*)$", ignore.case = TRUE)
yld_trace_site4 <- list.files(path = paste0(Growers_folder, site4),pattern = "trace(.*)$", ignore.case = TRUE)
 yld_trace_site5 <- list.files(path = paste0(Growers_folder, site5),pattern = "trace(.*)$", ignore.case = TRUE)
yld_trace_site6 <- list.files(path = paste0(Growers_folder, site6),pattern = "trace(.*)$", ignore.case = TRUE)
# yld_trace_site7 <- list.files(path = paste0(Growers_folder, site7),pattern = "trace(.*)$", ignore.case = TRUE)

#list files that conatin the word "final" followed by anything and ending with the word ".png": 

harvest_map_site1 <- list.files(path = paste0(Growers_folder, site1),pattern = "Final(.*)$", ignore.case = TRUE)
harvest_map_site2 <- list.files(path = paste0(Growers_folder, site2),pattern = "Final(.*)$", ignore.case = TRUE)
harvest_map_site3 <- list.files(path = paste0(Growers_folder, site3),pattern = "Final(.*)$", ignore.case = TRUE)
harvest_map_site4 <- list.files(path = paste0(Growers_folder, site4),pattern = "Final(.*)$", ignore.case = TRUE)
harvest_map_site5 <- list.files(path = paste0(Growers_folder, site5),pattern = "Final(.*)$", ignore.case = TRUE)
harvest_map_site6 <- list.files(path = paste0(Growers_folder, site6),pattern = "Final(.*)$", ignore.case = TRUE)
# harvest_map_site7 <- list.files(path = paste0(Growers_folder, site7),pattern = "Final(.*)$", ignore.case = TRUE)

### paddock id details
site_name_1 <- paste0("^",paddock_done2020$Farmer[1])
site_name_2 <- paste0("^",paddock_done2020$Farmer[2])
site_name_3 <- paste0("^",paddock_done2020$Farmer[3])
site_name_4 <- paste0("^",paddock_done2020$paddock[4])
site_name_5 <- paste0("^",paddock_done2020$paddock[5])
site_name_6 <- paste0("^",paddock_done2020$paddock[6])
# site_name_7 <- paste0("^",paddock_done2020$paddock[7])


Paddock_selected_site1 <- paddock_done2020$paddock[1]
Paddock_selected_site2 <- paddock_done2020$paddock[2]
Paddock_selected_site3 <- paddock_done2020$paddock[3]
Paddock_selected_site4 <- paddock_done2020$paddock[4]
Paddock_selected_site5 <- paddock_done2020$paddock[5]
Paddock_selected_site6 <- paddock_done2020$paddock[6]
# Paddock_selected_site7 <- paddock_done2020$paddock[7]


```

```{r read spatial data, message=FALSE, warning=FALSE, include=FALSE}
spatial_data_no_yld <- st_read("W:/value_soil_testing_prj/Yield_data/2020/All_Strips_2020_wgs84.shp")
spatial_data_no_yld_df <- data.frame(spatial_data_no_yld)
spatial_data_no_yld_df <- spatial_data_no_yld_df %>% dplyr::select(-geometry)

```
# Site 1

### Harvest map

```{r display site 1, echo=FALSE, message=FALSE, warning=FALSE}

include_graphics(paste0(Growers_folder,site1,  harvest_map_site1))
```


### Yield trace

```{r display site 1 yld trace, echo=FALSE, message=FALSE, warning=FALSE}
include_graphics(paste0(Growers_folder,site1,  yld_trace_site1))
```

### Results


```{r display results site 1, echo=FALSE, message=FALSE, warning=FALSE}

 image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site1)) %>% 
   image_rotate(90)

# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site1, ".+Pg1"))) %>% 
#   image_rotate(90)




```

```{r display results site 1 pag2, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site1)) %>% 
#   image_rotate(90)

# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site1, ".+Pg2"))) %>% 
#   image_rotate(90)
```



# Site 2

### Harvest map

```{r display site 2, echo=FALSE, message=FALSE, warning=FALSE}


include_graphics(paste0(Growers_folder,site2,  harvest_map_site2))
```
### Yield trace


```{r display site 2 yld trace, echo=FALSE, message=FALSE, warning=FALSE}


include_graphics(paste0(Growers_folder,site2,  yld_trace_site2))
```
### Results


```{r display results site 2 page1, echo=FALSE, message=FALSE, warning=FALSE}


image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site2)) %>%
  image_rotate(90)

# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site2, ".+Pg1"))) %>% 
#   image_rotate(90)

```

```{r display results site 2 page2, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}


# image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site2)) %>% 
#   image_rotate(90)

image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site2, ".+Pg2"))) %>% 
  image_rotate(90)

```

# Site 3

### Harvest map

```{r display site 3, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}


include_graphics(paste0(Growers_folder,site3,  harvest_map_site3))

```
### Yield trace


```{r display site 3 yld trace, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}


include_graphics(paste0(Growers_folder,site3,  yld_trace_site3))
```

### Results

```{r display results site 3 page1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}


# image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site3)) %>%
#   image_rotate(90)

# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site3, ".+Pg1"))) %>% 
#   image_rotate(90)

```

```{r display results site 3 page2, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}


# image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site3)) %>% 
#   image_rotate(90)

image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site3, ".+Pg2"))) %>% 
  image_rotate(90)

```

# Site 4

### Harvest map

```{r display site 4, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}



include_graphics(paste0(Growers_folder,site4,  harvest_map_site4))
```


### Yield trace

```{r display site 4 yld trace, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

include_graphics(paste0(Growers_folder,site4,  yld_trace_site4))
```


### Results

```{r display results site 4 Page 1, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site4)) %>%
#   image_rotate(90)


# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site4, ".+Pg1"))) %>% 
#   image_rotate(90)


```



```{r display site 5, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# Site 5

### Harvest map


include_graphics(paste0(Growers_folder,site5,  harvest_map_site5))
```


```{r display site 5 yld trace, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

### Yield trace


include_graphics(paste0(Growers_folder,site5,  yld_trace_site5))
```


```{r display results site 5 page 1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
### Results



 image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site5)) %>% 
   image_rotate(90)


# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site5, ".+Pg1"))) %>% 
#   image_rotate(90)

```





```{r "display site 6", eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Site 6

### Harvest map


include_graphics(paste0(Growers_folder,site6,  harvest_map_site6))
```




```{r "display site 6 yld trace", eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

### Yield trace

include_graphics(paste0(Growers_folder,site6,  yld_trace_site6))
```


```{r display results site 6 page 1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

### Results


image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site6)) %>%
  image_rotate(90)

# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site6, ".+Pg1"))) %>% 
#   image_rotate(90)

```





```{r display site 7, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Site 7

### Harvest map

include_graphics(paste0(Growers_folder,site7,  harvest_map_site7))
```




```{r "display site 7 yld trace", eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
### Yield trace


include_graphics(paste0(Growers_folder,site7,  yld_trace_site7))
```



```{r "display results site 7 page 1", eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
### Results


image_read(dir(png_folder, full.names=T, pattern=Paddock_selected_site7)) %>%
  image_rotate(90)

# image_read(dir(png_folder, full.names=T, pattern = paste0(Paddock_selected_site7, ".+Pg1"))) %>% 
#   image_rotate(90)


```


# Checks for CSIRO 

### check the rate provided is equivalent to the calculated N/P content.

```{r how many sites, message=FALSE, warning=FALSE, include=FALSE}


numb_sites_paddock_ID <- c(Paddock_selected_site1, Paddock_selected_site2)
numb_sites_paddock_ID


```

```{r checks site , echo=FALSE, message=FALSE, warning=FALSE}

fert_applied <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/processing_files/step2_fert_app_select_clm.csv")




check_fert_applied <- fert_applied %>%
  dplyr::filter(
    Paddock_ID %in% numb_sites_paddock_ID) %>%
  dplyr::select(Paddock_ID,
                Rate,
                Strip_Rate,
                Strip_Type,
                Total_sum_N_content,
                Total_sum_P_content) %>%
  arrange(Paddock_ID, Rate)


check_fert_applied$Total_sum_N_content <- round(check_fert_applied$Total_sum_N_content, 2)
check_fert_applied$Total_sum_P_content <- round(check_fert_applied$Total_sum_P_content, 2)


check_fert_applied <- left_join(check_fert_applied,
                                paddock_details,
                                by = c("Paddock_ID" = "paddock5_digits"))
#! we have a problem with "524102" in  check_fert_applied and  52410 in paddock_details (5 digits)
#So when Paddock ID 52410 I will enter the farmer and paddoock tested Farmer = Pole	, `Paddock tested` = Gums
# check_fert_applied <- check_fert_applied %>% 
#   mutate(Farmer = case_when(
#     Paddock_ID == 524102 ~ "Pole",
#     TRUE ~ Farmer)) %>% 
#   mutate(`Paddock tested` = case_when(
#     Paddock_ID == 524102 ~ "Gums",
#     TRUE ~ `Paddock tested`))


check_fert_applied <- check_fert_applied %>% 
  dplyr::select(`Paddock ID` = Paddock_ID,
                #`Zone name` = Zone,
                Farmer, 
                `Paddock tested`,
                `Strip Type` = Strip_Type,
                `Strip Rate` = Strip_Rate,
                `N content` = Total_sum_N_content,
                `P content` = Total_sum_P_content)


#check_fert_applied <-check_fert_applied[!duplicated(check_fert_applied$'Strip Rate'), ]
check_fert_applied <-distinct_at(check_fert_applied, vars(`Strip Rate`,`Paddock tested`), .keep_all = TRUE)

check_fert_applied <- check_fert_applied %>% arrange(`Paddock ID`, `N content`)

check_fert_applied %>% 
  formattable(align = "l", - 1  )
```

## Comments from the spatial data

```{r comments on spatial data 2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="List of all unique comments in spatial dataset"}


comments_frm_spatial_data <- spatial_data_no_yld_df %>% 
  dplyr::filter(
    Paddock_ID %in% numb_sites_paddock_ID) %>%
  
distinct( paddock,Comments, .keep_all = TRUE) %>% 
  dplyr::select(Paddock_ID ,farmer, paddock, Comments )

comments_frm_spatial_data %>% 
  formattable(align = "l", - 1  )
```

# Comparison of yield response: Growers standard practice strips (GSP vs Alt GSP)

Ideally the yield would be the same in both strips (GSP and Alt GSP), and / or the yield would not be significantly different.



Significant yield differences between the two strips suggest that there is a high degree of variability between the two strip that were applied with the same fertiliser.

This may occur because the strips have underlying soil, plant growth conditions.


```{r plot2 alt strips results, echo=FALSE, message=FALSE, warning=FALSE}
GSP_AltGSP_t_test <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/GSP_AltGSP_t_test_merged_3c.csv")

 

GSPvsAltGSP_plot <- GSP_AltGSP_t_test %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) %>%
    
  ggplot( mapping = aes(x=Significant_practical ))+
  geom_bar() +
  facet_grid(.~ Strip_Type)+
  theme_bw()+
  labs(title = "Comparison of yield response in strips with the same fertiliser rate",
       subtitle = "Strip with growers standard practice vs alternative growers standard practice",
       y = "Count of zones with a significant difference",
       x = "result of t - test (GSP vs. Alt GSP)")

GSPvsAltGSP_plot







```

### Detailed results of GSP vs Alt GSP

```{r table alt strips results, echo=FALSE, message=FALSE, warning=FALSE,fig.cap = "mean difference between the 2 GSP strips"}



GSP_AltGSP_t_test_display <- GSP_AltGSP_t_test %>% 
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
  


GSP_AltGSP_t_test_display <- left_join(GSP_AltGSP_t_test_display,
                                       paddock_details, by = c("Zone_ID" = "Paddock code"))



GSP_AltGSP_t_test_display <- GSP_AltGSP_t_test_display %>%  
  dplyr::select(`Zone ID` =   Zone_ID, 
                `Zone name` = Zone.x, 
                 Farmer,
                `Paddock tested`,
                #`yield response` = yld_response, 
                `Mean yield difference` = rounded, 
                `Significant` = Significant_practical
                ) 
GSP_AltGSP_t_test_display <- GSP_AltGSP_t_test_display %>% 
  arrange(`Zone ID`)


GSP_AltGSP_t_test_display %>% 
  formattable(align = "l", - 1  )
```




# Comparison of yield response: High medium and low fertiliser rates

Different comparisons are made between high, medium and low fertiliser rates for each zone.

Comparison of yield response in the strip / zone per paddock between:

- High fertiliser rate vs low fertiliser rate (yield for high fert rate - yield for low fert rate)
- High fertiliser rate vs medium fertiliser rate (yield for high fert rate - yield for medium fert rate)
- Medium fertiliser rate vs low fertiliser rate (yield for medium fert rate - yield for low fert rate)

- **The yield response is classed as 'positive' when higher rates of fertiliser results in higher yields.**

- The yield response is classed as 'no response' when higher rates of fertiliser results in no change in yields (this is defined as 0 +/- standard error)

- The yield response is classed as 'negative' when higher rates of fertiliser results in lower yields.

T- test was also run for each comparison and the significant differences at p < 0.05 reported.
Note that some significant values are not reported for the zone, this may occur when there is not enough data points to run the t - test (although there is still have yield values to make a comparison). 




The below table shows what fertiliser rates were assigned to low medium and high fertiliser rates.



```{r what is defined as high low , echo=FALSE, message=FALSE, warning=FALSE}

high_low_comp <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/hign_low_t_test_merged_3b.csv")

high_low_comp <- high_low_comp %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
  #   paddock_ID == Paddock_selected_site1 |
  #     paddock_ID == Paddock_selected_site2 |
  #     paddock_ID == Paddock_selected_site3|
  #     paddock_ID == Paddock_selected_site4 
  #     # paddock_ID == Paddock_selected_site5
  #     # paddock_ID == Paddock_selected_site6 |
  #     # paddock_ID == Paddock_selected_site7
  # )
high_low_comp <- left_join(high_low_comp,
                  paddock_details, by = c("Zone_ID" = "Paddock code"))

high_low_comp_define <-distinct(high_low_comp,paddock_ID, .keep_all = TRUE  ) %>% 
  dplyr::select(`paddock ID` = paddock_ID,
                Farmer,
                `Paddock tested`,
                'rate low' = rate_low,
                'rate medium' = rate_medium,
                'rate high' = rate_high,
                'rate very high' = rate_very_high)

rate_used <- paddock_done2020 %>% 
  distinct(paddock, .keep_all= TRUE) %>% 
  dplyr::select(paddock ,
                "Rates used (low med high analysis)") %>% 
  mutate(paddock = as.double(paddock))

high_low_comp_define <- left_join(high_low_comp_define, rate_used, by= c("paddock ID" = "paddock"))

high_low_comp_define <- high_low_comp_define %>% 
  arrange(`paddock ID`)

high_low_comp_define %>% 
  formattable(align = "l", - 1  )




```


```{r high med low comparision, echo=FALSE, message=FALSE, warning=FALSE}

                        


high_low_comp$comparison <-
  factor(
    high_low_comp$comparison,
    levels = c("high_v_low", "high_v_medium", "medium_v_low"),
    labels = c(
      "high fert vs low fert",
      "high fert vs medium fert",
      "medium fert vs low fert"
    )
  )


high_low_plot <-
  filter(high_low_comp, Significant_practical != "NA") %>% 
  ggplot( mapping = aes(x = yld_response, fill = Significant_practical)) +
  geom_bar() +
  facet_grid(Strip_Type ~ comparison)+ 
  theme_bw() +
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  scale_x_discrete(
    labels = c(
      "positive" = "positive",
      "no_response" = "no response",
      "negative" = "negative"
    )
  ) +
  #scale_fill_discrete(name="t.test result \npractical")+
  scale_fill_discrete(name="t.test result ")+
    labs(
    title = "Comparison of yield response in strips with different fertiliser rate",
    subtitle = "The yield response is classed as positive when higher rates of fertiliser result in higher yields",
    caption = "note: only comparison that support t.test analysis displayed",
     y = "Count of paddocks in yield response class",
    x = "yield response"
  )
high_low_plot

```

### High fertiliser rate vs low fertiliser rate.

```{r high vs low table part1, echo=FALSE, message=FALSE, warning=FALSE}
#high low med comp high vs low  table rates

high_low_comp_t <- read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/hign_low_t_test_merged_3b.csv")

high_low_comp_t <- high_low_comp_t %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID)
  
high_low_comp_t <- left_join(high_low_comp_t,
                           paddock_details, by = c("Zone_ID" = "Paddock code"))



high_v_low_comp_results <- high_low_comp_t %>% 
  filter(comparison == "high_v_low") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `zone name` = Zone.y ,
                Farmer,
                `Paddock tested`,
                "yield response" = yld_response,
                `Significant` = Significant_practical) 
high_v_low_comp_results <- high_v_low_comp_results %>% 
  arrange(`Zone ID`)



high_v_low_comp_results %>% 
  formattable(align = "l", - 1  )

```

### High fertiliser rate vs medium fertiliser rate.

```{r high vs medium  table part2, echo=FALSE, message=FALSE, warning=FALSE}

high_v_med_comp_results <- high_low_comp_t %>% 
  filter(comparison == "high_v_medium") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `zone name` = Zone.y ,
                Farmer,
                `Paddock tested`,
                "yield response" = yld_response,
                `Significant` = Significant_practical) 
high_v_med_comp_results <- high_v_med_comp_results %>% 
  arrange(`Zone ID`)

high_v_med_comp_results %>% 
  formattable(align = "l", - 1  )
```

### Medium fertiliser rate vs low fertiliser rate.

```{r medium vs low  table part3, echo=FALSE, message=FALSE, warning=FALSE}

med_v_low_comp_results <- high_low_comp_t %>% 
  filter(comparison == "medium_v_low") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `zone name` = Zone.y ,
                Farmer,
                `Paddock tested`,
                "yield response" = yld_response,
                `Significant` = Significant_practical) 
med_v_low_comp_results <- med_v_low_comp_results %>% 
  arrange(`Zone ID`)

med_v_low_comp_results %>% 
  formattable(align = "l", - 1  )

```

# Comparison of yield response: the growers fertilisers rate of application vs. higher or lower fertilisers rates.


Different comparisons are made between the growers standard practice and fertilisers strips for each zone.

Comparison of yield response in the strip / zone per paddock between:

- Growers standard practice GSP  vs low fertiliser rate (yield for GSP fert rate - yield for low fert rate)
- Growers standard practice GSP  fertiliser rate vs high fertiliser rate (yield for GSP fert rate - yield for high fert rate)


The yield response is classed as 'positive' when higher rates of fertiliser results in higher yields

The yield response is classed as 'no response' when higher rates of fertiliser results in no change in yields (this is defined as 0 +/- standard error)

The yield response is classed as 'negative' when higher rates of fertiliser results in lower yields.

T- test was also run for each comparison and the significant differences at p < 0.05 reported.
Note that some significant values are not reported for the zone, this may occur when there is not enough data points to run the t - test (although there is still have yield values to make a comparison). 


The below table details what rates were excluded from the analysis.
For sites with more than 3 rates one strip rate was exuded from the analysis.

If this should be a different rate and not the one excluded the analysis will need to be re - run.
Please make a note.







```{r GR comp high low plot, echo=FALSE, message=FALSE, warning=FALSE}

                      

GR_comparison <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/GSP_low_high_comparision_t_test_merged_3d.csv")
GR_comparison <- GR_comparison %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
  #   paddock_ID == Paddock_selected_site1 |
  #     paddock_ID == Paddock_selected_site2 |
  #     paddock_ID == Paddock_selected_site3|
  #     paddock_ID == Paddock_selected_site4 
  #     # paddock_ID == Paddock_selected_site5
  #      # paddock_ID == Paddock_selected_site6 |
  #      # paddock_ID == Paddock_selected_site7
  # )

GR_comparison_plot <-
  filter(GR_comparison, Significant_practical != "NA") %>%
  ggplot( mapping = aes(x = yld_response, fill = Significant_practical)) +
  geom_bar() +
  facet_grid(Strip_Type ~ comparison)+ 
  #labeller(Strip_Type = label_wrap_gen(width = 16 ),
  #         comparison = label_wrap_gen(width = 16))) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  scale_x_discrete(
    labels = c(
      "positive" = "positive",
      "no_response" = "no response",
      "negative" = "negative"
    )
  ) +
  #scale_fill_discrete(name="t.test result \npractical")+
  scale_fill_discrete(name="t.test result")+
    labs(
    title = "Comparison of yield response for GSP VS higher/lower rates",
    subtitle = "The yield response is classed as positive when higher rates of fertiliser result in higher yields",
    caption = "note: only comparison that support t.test analysis displayed",
     y = "Count of paddocks in yield response class",
    x = "yield response"
  )

GR_comparison_plot



```

### GSP vs higher fertiliser rates
#### The rates were used for the analysis



```{r GPS  comp high table rates, echo=FALSE, message=FALSE, warning=FALSE}


GR_comparison <- left_join(GR_comparison, paddock_details, by= c("Zone_ID" = "Paddock code"))


GR_comparison_higher_rates <- GR_comparison %>% 
  filter(comparison == "GSP_v_high") %>% 
  dplyr::select('Zone ID' = Zone_ID,
                #comparison,
                Farmer,
                `Paddock tested`,
                `GSP rate` = "the_GSP_label",
                `higher than GSP rate` = "higher_than_GSP_label") %>% 
  arrange(`Zone ID`)


GR_comparison_higher_results <- GR_comparison %>% 
  filter(comparison == "GSP_v_high") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `zone name` = Zone.y ,
                Farmer,
                `Paddock tested`,
                "yield response" = yld_response,
                `Significant` = Significant_practical) 


GR_comparison_higher_results <- GR_comparison_higher_results %>% 
  arrange(`Zone ID`)


GR_comparison_higher_rates %>% 
  formattable(align = "l", - 1  )
```

#### The results for the analysis
```{r GPS comp high table results, echo=FALSE, message=FALSE, warning=FALSE}


GR_comparison_higher_results %>% 
   formattable(align = "l", - 1  )

```

### GSP vs lower fertiliser rates
#### The rates were used for the analysis

```{r GPS  comp lower table rates, echo=FALSE, message=FALSE, warning=FALSE}




GR_comparison_lower_rates <- GR_comparison %>% 
  filter(comparison == "GSP_v_low") %>% 
  dplyr::select('Zone ID' = Zone_ID,
                #comparison,
                `zone name` = Zone.y ,
                Farmer,
                `Paddock tested`,
                `GSP rate` = "the_GSP_label",
                `lower than GSP rate` = "lower_than_GSP_label") %>% 
  arrange(`Zone ID`)


GR_comparison_lower_results <- GR_comparison %>% 
  filter(comparison == "GSP_v_low") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `zone name` = Zone.y ,
                Farmer,
                `Paddock tested`,
                "yield response" = yld_response,
                `Significant` = Significant_practical) 


GR_comparison_lower_results <- GR_comparison_lower_results %>% 
  arrange(`Zone ID`)

GR_comparison_lower_rates %>% 
   formattable(align = "l", - 1  )

```


#### The results for the analysis
```{r GPS comp lower table results, echo=FALSE, message=FALSE, warning=FALSE}


GR_comparison_lower_results %>% 
   formattable(align = "l", - 1  )

```

# Comparison of yield response: The closest match to recommended fertiliser rates compared to higher and lower fertiliser rates.

The soil test results results in a recommended N and P rate.

Sean has done these calculations.

The recommended fertiliser rate was not always implemented, so I have worked out the closest match.


The approx recommended rate:

A = recommend rate - abs(rate 1)

B = recommend rate - abs(rate 2)

C =  rate - abs(rate 3)


Then work out which has the smallest value A, B or C, this will be the approx recommended rate.

Then I assigned a rate lower and a rate higher than recommend rate for the comparison.

Higher and lower rates won't always exist, for some paddocks.

In some cases the rates will all be higher or all be lower, while for other paddocks there will be choice to be made (which rates should be used).

If we need to choose what rates to induced it is best to use this rough rule:

- Avoid 0 rates (won't always be practical)
- lower rate should be close to half the recommended rate
- higher rate should be close to double the  rate.



Comparison of yield response in the strip / zone per paddock between:

- Approx recommend rate  vs lower fertiliser rate 

  (yield for app rec fertiliser rate - yield for lower fertiliser rate)

- Approx recommend rate  fertiliser rate vs higher fertiliser rate 

  (yield for app rec fertiliser rate - yield for higher fertiliser rate)

### The results:

The yield response is classed as 'positive' when higher rates of fertiliser results in higher yields

The yield response is classed as 'no response' when higher rates of fertiliser results in no change in yields (this is defined as 0 +/- standard error)

The yield response is classed as 'negative' when higher rates of fertiliser results in lower yields.

T- test was also run for each comparison and the significant differences at p < 0.05 reported.
Note that some significant values are not reported for the zone, this may occur when there is not enough data points to run the t - test (although there is still have yield values to make a comparison). 


The below table details what rates were excluded from the analysis.

If this should be a different rate and not the one excluded the analysis will need to be re - run.
Please make a note.


```{r rec rate comp high low plot, echo=FALSE, message=FALSE, warning=FALSE}

Rec_rate_comparison <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/rec_rate_low_high_comparision_t_test_merged_3e.csv")

              

Rec_rate_comparison <- Rec_rate_comparison %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
    # paddock_ID == Paddock_selected_site1 |
    #   paddock_ID == Paddock_selected_site2 |
    #   paddock_ID == Paddock_selected_site3|
    #   paddock_ID == Paddock_selected_site4 
      # paddock_ID == Paddock_selected_site5
      # paddock_ID == Paddock_selected_site6 |
      # paddock_ID == Paddock_selected_site7
#  )

Rec_rate_comparison_plot <-
  filter(Rec_rate_comparison, yld_response != "NA") %>%
  ggplot( mapping = aes(x = yld_response, fill = Significant_practical)) +
  geom_bar() +
  facet_grid(Strip_Type ~ comparison)+ 
  #labeller(Strip_Type = label_wrap_gen(width = 16 ),
  #         comparison = label_wrap_gen(width = 16))) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  
  scale_x_discrete(
    labels = c(
      "positive" = "positive",
      "no_response" = "no response",
      "negative" = "negative"
    )
  ) +
  scale_fill_discrete(name="t.test result \npractical")+
  labs(
    title = "Comparison of yield response for approx. recommended rate vs higher/lower rates (P)",
    subtitle = "The yield response is classed as positive when higher rates of fertiliser result in higher yields",
    caption = "note: only comparison that support t.test analysis displayed",
     y = "Count of paddocks in yield response class",
    x = "yield response"
  )


Rec_rate_comparison_plot





```


```{r rec rate comp high low plot N, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

Rec_rate_comparison_N <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/rec_rate_low_high_comparision_t_test_merged_3e_N.csv")

              

Rec_rate_comparison_N <- Rec_rate_comparison_N %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID)
    # paddock_ID == Paddock_selected_site1 |
    #   paddock_ID == Paddock_selected_site2 |
    #   paddock_ID == Paddock_selected_site3|
    #   paddock_ID == Paddock_selected_site4 
      # paddock_ID == Paddock_selected_site5
      # paddock_ID == Paddock_selected_site6 |
      # paddock_ID == Paddock_selected_site7
 # )

Rec_rate_comparison_plot_N <-
  filter(Rec_rate_comparison_N, yld_response != "NA") %>%
  ggplot( mapping = aes(x = yld_response, fill = Significant_practical)) +
  geom_bar() +
  facet_grid(Strip_Type ~ comparison)+ 
  #labeller(Strip_Type = label_wrap_gen(width = 16 ),
  #         comparison = label_wrap_gen(width = 16))) +
  theme_bw() +
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  
  scale_x_discrete(
    labels = c(
      "positive" = "positive",
      "no_response" = "no response",
      "negative" = "negative"
    )
  ) +
  scale_fill_discrete(name="t.test result \npractical")+
  labs(
    title = "Comparison of yield response for approx. recommended rate vs higher/lower rates (N)",
    subtitle = "The yield response is classed as positive when higher rates of fertiliser result in higher yields",
    caption = "note: only comparison that support t.test analysis displayed",
     y = "Count of paddocks in yield response class",
    x = "yield response"
  )


Rec_rate_comparison_plot_N





```


### Approx recommended rate vs higher fertiliser rates
#### The rates were used for the analysis





```{r rec rate comp high table rates N P, echo=FALSE, message=FALSE, warning=FALSE}

#using the padock code and zone ID
paddock_details_join <- distinct(paddock_details, `Paddock code`, .keep_all = TRUE)


## just subset the sites we are looking at
paddock_details_join <- paddock_details_join %>%
  dplyr::filter(
    paddock5_digits %in% numb_sites_paddock_ID) 
  
## just subset the clm we want
paddock_details_join <- paddock_details_join %>%  
  dplyr::select(`Zone ID`=`Paddock code`, `Paddock tested`,  `Zone name` =  Zone )
paddock_details_join <- as.data.frame(paddock_details_join)
 

Rec_rate_comparison_N <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/rec_rate_low_high_comparision_t_test_merged_3e_N.csv")

Rec_rate_comparison_N <- Rec_rate_comparison_N %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
 


Rec_rate_comparison_N <- left_join(Rec_rate_comparison_N, paddock_details_join, by= c("Zone_ID" = "Zone ID"))
# #! we have a problem with "524102" in  check_fert_applied and  52410 in paddock_details (5 digits)
# #So when Paddock ID 52410 I will enter the farmer and paddoock tested Farmer = Pole	, `Paddock tested` = Gums
 # Rec_rate_comparison_N <- Rec_rate_comparison_N %>% 
 #   mutate(`Paddock tested` = case_when(
 #     paddock_ID == 524102 ~ "Gums",
 #     TRUE ~ `Paddock tested`))

#str(paddock_details_join)
#str(Rec_rate_comparison_N)

Rec_rate_comparison_table_higher_rates_N <- Rec_rate_comparison_N %>% 
  filter(comparison == "rec_n_v_higher") %>% 
  dplyr::select('Zone ID' = Zone_ID,
                #Farmer ,
                `Paddock tested`, 
                `Strip Type`=`Strip_Type`,
                #comparison,
                `approx recommed rate` = "rec_rate_n_label",
                `higher than recommed rate` = "higher_than_rec_rate_n_label") %>% 
  arrange(`Zone ID`)

Rec_rate_comparison_table_higher_results_N <- Rec_rate_comparison_N %>% 
  filter(comparison == "rec_n_v_higher") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `Zone name` ,
                #Farmer,
                `Paddock tested`,
                `Strip Type`=`Strip_Type`,
                "yield response" = yld_response,
                `Significant practical` = Significant_practical) 


Rec_rate_comparison_table_higher_results_N <- Rec_rate_comparison_table_higher_results_N %>% 
  arrange(`Zone ID`, `Strip Type`)



###################################################################################################
Rec_rate_comparison <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/rec_rate_low_high_comparision_t_test_merged_3e.csv")
Rec_rate_comparison <- Rec_rate_comparison %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
    


Rec_rate_comparison <- left_join(Rec_rate_comparison, paddock_details_join, by= c("Zone_ID" = "Zone ID"))

#! we have a problem with "524102" in  check_fert_applied and  52410 in paddock_details (5 digits)
#So when Paddock ID 52410 I will enter the farmer and paddoock tested Farmer = Pole	, `Paddock tested` = Gums


#str(paddock_details_join)
#str(Rec_rate_comparison_N)

Rec_rate_comparison_table_higher_rates <- Rec_rate_comparison %>% 
  filter(comparison == "rec_p_v_higher") %>% 
  dplyr::select('Zone ID' = Zone_ID,
                #Farmer ,
                `Paddock tested`, 
                `Strip Type`=`Strip_Type`,
                #comparison,
                `approx recommed rate` = "rec_rate_p_label",
                `higher than recommed rate` = "higher_than_rec_rate_p_label") %>% 
  arrange(`Zone ID`)

Rec_rate_comparison_table_results <- Rec_rate_comparison %>% 
  filter(comparison == "rec_p_v_higher") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `Zone name` ,
                #Farmer,
                `Paddock tested`,
                `Strip Type`=`Strip_Type`,
                "yield response" = yld_response,
                `Significant practical` = Significant_practical) 

####################################################################################################
# Rec_rate_comparison_table_higher_results_N
# Rec_rate_comparison_table_higher_rates_N
# Rec_rate_comparison_table_higher_rates
# Rec_rate_comparison_table_results


Rec_rate_comparison_table_results <- rbind(Rec_rate_comparison_table_results,
                                           Rec_rate_comparison_table_higher_results_N)



Rec_rate_comparison_table_higher_rates <- rbind(Rec_rate_comparison_table_higher_rates,
                                                Rec_rate_comparison_table_higher_rates_N)


Rec_rate_comparison_table_higher_rates %>% 
   formattable(align = "l", - 1  )
                
```


#### The results for the analysis

```{r rec rate comp high table results, echo=FALSE, message=FALSE, warning=FALSE}



Rec_rate_comparison_table_results %>% 
   formattable(align = "l", - 1  )



```

### Approx recommended rate vs lower fertiliser rates
#### The rates were used for the analysis



```{r rec rate comp low table N P , echo=FALSE, message=FALSE, warning=FALSE}

Rec_rate_comparison_N <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/rec_rate_low_high_comparision_t_test_merged_3e_N.csv")

Rec_rate_comparison_N <- Rec_rate_comparison_N %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
  


Rec_rate_comparison_N <- left_join(Rec_rate_comparison_N, paddock_details_join, by= c("Zone_ID" = "Zone ID"))
# #! we have a problem with "524102" in  check_fert_applied and  52410 in paddock_details (5 digits)
# #So when Paddock ID 52410 I will enter the farmer and paddoock tested Farmer = Pole	, `Paddock tested` = Gums
 Rec_rate_comparison_N <- Rec_rate_comparison_N %>% 
   mutate(`Paddock tested` = case_when(
     paddock_ID == 524102 ~ "Gums",
     TRUE ~ `Paddock tested`))


Rec_rate_comparison_table_lower_rates_N <- Rec_rate_comparison_N %>% 
  filter(comparison == "rec_n_v_lower") %>% 
  dplyr::select('Zone ID' = Zone_ID,
                #Farmer ,
                `Paddock tested`, 
                `Strip Type`=`Strip_Type`,
                #comparison,
                `approx recommed rate` = "rec_rate_n_label",
                `lower than recommed rate` = "lower_than_rec_rate_n_label") %>% 
  arrange(`Zone ID`)

Rec_rate_comparison_table_lower_results_N <- Rec_rate_comparison_N %>% 
  filter(comparison == "rec_n_v_lower") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `Zone name` ,
                #Farmer,
                `Paddock tested`,
                `Strip Type`=`Strip_Type`,
                "yield response" = yld_response,
                `Significant practical` = Significant_practical) 


Rec_rate_comparison_table_lower_results_N <- Rec_rate_comparison_table_lower_results_N %>% 
  arrange(`Zone ID`, `Strip Type`)



###################################################################################################
Rec_rate_comparison <-  read.csv("W:/value_soil_testing_prj/Yield_data/2020/processing/r_outputs/merged_comparision_output/rec_rate_low_high_comparision_t_test_merged_3e.csv")
Rec_rate_comparison <- Rec_rate_comparison %>%
  dplyr::filter(
    paddock_ID %in% numb_sites_paddock_ID) 
  


Rec_rate_comparison <- left_join(Rec_rate_comparison, paddock_details_join, by= c("Zone_ID" = "Zone ID"))

#str(paddock_details_join)
#str(Rec_rate_comparison_N)

Rec_rate_comparison_table_lower_rates <- Rec_rate_comparison %>% 
  filter(comparison == "rec_p_v_lower") %>% 
  dplyr::select('Zone ID' = Zone_ID,
                #Farmer ,
                `Paddock tested`, 
                `Strip Type`=`Strip_Type`,
                #comparison,
                `approx recommed rate` = "rec_rate_p_label",
                `lower than recommed rate` = "lower_than_rec_rate_p_label") %>% 
  arrange(`Zone ID`)

Rec_rate_comparison_table_lower_results <- Rec_rate_comparison %>% 
  filter(comparison == "rec_p_v_lower") %>%  
  dplyr::select('Zone ID' = Zone_ID,
                `Zone name` ,
                #Farmer,
                `Paddock tested`,
                `Strip Type`=`Strip_Type`,
                "yield response" = yld_response,
                `Significant practical` = Significant_practical) 

####################################################################################################
# Rec_rate_comparison_table_higher_results_N
# Rec_rate_comparison_table_higher_rates_N
# Rec_rate_comparison_table_higher_rates
# Rec_rate_comparison_table_results


 Rec_rate_comparison_table_lower_results <- rbind(Rec_rate_comparison_table_lower_results,
                                            Rec_rate_comparison_table_lower_results_N)



 Rec_rate_comparison_table_lower_rates <- rbind(Rec_rate_comparison_table_lower_rates,
                                                 Rec_rate_comparison_table_lower_rates_N)


Rec_rate_comparison_table_lower_rates %>% 
   formattable(align = "l", - 1  )

                
```

#### The results for the analysis

```{r rec rate comp low table results, echo=FALSE, message=FALSE, warning=FALSE}
Rec_rate_comparison_table_lower_results %>% 
   formattable(align = "l", - 1  )



```


# Action required : 


1. Review that the results look sensible and nothing needs re running - are the reports OK to send off?

2. The fertiliser applied has translated correctly to units of N or P.

3. Are the rates included in the comparison analysis sensible and what you want.

3. Are the paddocks to be included in the economics analysis?



Notes should be made in the below file:

[For Notes ]("C:/Users/ouz001/CSIRO/Ratcliff, Christina (A&F, Waite Campus) - Soil_Testing_Project/paddock_done2020.xlsx")


# Couple of checks and comments from Sean and Harms database.
```{r Sean and Harms DB, echo=FALSE, message=FALSE, warning=FALSE}

recom_rateDB <- read_excel( "W:/value_soil_testing_prj/Yield_data/2020/processing/GRDC 2020 Paddock Database_SA_VIC_May05 2021.xlsx")
##########################################################################################################################################


recom_rateDB <- recom_rateDB %>% 
  dplyr::select(Zone_ID =    `Paddock code` ,
                p_rec =           `P rec`,
                n_rec_yld_low =   `N Rec (< 3 t/ha)` ,       
                n_rec_yld_med =   `N Rec (3-5 t/ha)` ,             
                n_rec_yld_high =  `N Rec (> 5 t/ha)`,
                SM_comment_Soil_N = `SM comment Soil N`,
                SM_comment_Soil_P = `SM comment Soil P`,
                SM_comment_Plant_Tissue = `SM comment Plant Tissue`
  ) 

recom_rateDB <-  dplyr::mutate(recom_rateDB,  maxN = apply(recom_rateDB[3:5], 1, max, na.rm = TRUE))

recom_rateDB$Zone_ID <- as.double(recom_rateDB$Zone_ID)

# remove redunant clm and replace inf
recom_rateDB <- recom_rateDB %>% 
  mutate(
    maxN = case_when(
      maxN >= 0 ~ maxN,
      TRUE ~ NA_real_
    )
  )


## add 5 digit paddock code to data farme
recom_rateDB <- recom_rateDB %>% 
  dplyr::mutate(paddock5_digits = substr(Zone_ID, start = 1, stop = 5))

#select only the paddocks we are working with
recom_rateDB <- recom_rateDB %>%
  dplyr::filter(
    paddock5_digits %in% numb_sites_paddock_ID) 
    



recom_rateDB <- left_join(recom_rateDB,
                                       paddock_details, by = c("Zone_ID" = "Paddock code"))

recom_rateDB <- recom_rateDB %>% 
  dplyr::select( `Zone ID` = Zone_ID,
                 #Farmer,
                 `Paddock tested`,
                 Zone,
                 `p rec` = p_rec,
                 `Comment Soil P` = SM_comment_Soil_P,
                 `n rec` = maxN,
                 `Comment Soil N` = SM_comment_Soil_N,
                 `Comment Plant Tissue` = SM_comment_Plant_Tissue,
                 n_rec_yld_low,
                 n_rec_yld_med,
                 n_rec_yld_high)



recom_rateDB %>% 
  formattable(align = "l", - 1  )


```

